---
title: "Evan WB - Homework 1"
author: "Evan Woelk Balzer"
date: "07/01/2020"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r Loading in packages}
library(tidyverse)
library(matrixStats)
```

#Question 1#
```{r Generating vectors for each strain}
TsA <- c(0.17, 0.20, 0.13, 0.20, 0.24, 0.25, 0.15, 0.21, 0.21)
TsA

TsB <- c(0.47, 0.21, 0.34, 0.32, 0.33, 0.29, 0.18, 0.20, 0.25)
TsB

Cs <- c(0.44, 0.33, 0.37, 0.33, 0.31, 0.27, 0.22, 0.30, 0.28)
Cs

strains <- tibble(TsA, TsB, Cs)
strains
```

#Question 2, 3#
```{r Generating and comparing mean objects}
mtsa <- mean(TsA)
mtsb <- mean(TsB)
mcs <- mean(Cs)

mabdif <- (mtsb - mtsa)
mabdif

mcadif <- (mcs - mtsa)
mcadif
```
The difference between the means of the two transgenic strains is 0.09222.
The difference between the means of the transgenic strain A and the common strain is 1.1211.

#Question 4#
```{r Plotting a histogram}
a <- ggplot(strains, aes(Cs))
#getting the same breaks as given by the standard hist command#
brx <- pretty(range(strains$Cs), n = nclass.Sturges(strains$Cs),min.n = 1)
ggcommonhist <- a+geom_histogram(breaks = brx, alpha = 0.5, color = "black")+labs(x = "Concentration", y = "Count")+theme_classic()+scale_x_continuous(breaks = seq(0,1, 0.05))
ggcommonhist
```

#Question 5#
```{r Building the growth and peroxide vectors}
Peroxide <- c(0.27, 0.21, 0.34, 0.32, 0.24, 0.29, 0.18, 0.20, 0.29)
Growth.rate <- c(1.79, 1.01, 1.71, 1.89, 1.41, 1.15, 1.13, 1.20, 1.10)
pergro <- tibble(Peroxide, Growth.rate)
```

#Question 6#
```{r Plotting hydrogen peroxide against fungal growth}
b <- ggplot(pergro, aes(Peroxide, Growth.rate))
pergroscatter <- b+geom_point()+theme_classic()+labs(x = "Hydrogen Peroxide Concentration (μmoles/g)", y = "Growth Rate (cm/day)")+geom_smooth(method='lm')
pergroscatter
```

#Question 7#

As the concentration of hydrogen peroxide increases, so does the growth rate of the fungus. This result contradicts the hypothesis, suggesting that this application of hydrogen peroxide promotes fungal growth.

#Question 8, 9#
```{r Reading in the turtle data and making individual contingency tables}
trep <- read_csv("turtle_reproduction.csv", col_names = (TRUE), col_types = cols(Nesting_Success = "f", Species = "f"))
contingency_trep <- table(trep)
contingency_trep
```

#Question 10#
```{r }
b <- ggplot(trep, aes(x = Species, fill = Nesting_Success))
turtletable <- b+geom_bar(position = "dodge")+scale_fill_manual(name = "Nesting Outcome", values = c("green4", "firebrick3"))+theme_classic()+scale_y_continuous("Number of Nesting Attempts")
turtletable
```

#Question 11#
```{r Finding the mean and standard deviation for successes}
asd<- table(trep)
asd

samean <-rowMeans(asd)
samean

sasd <- rowSds(asd)
sasd
```
Across all three species, the mean number of nesting successes is 8 the standard deviation of nesting success is 6.928.

#Question 12#
```{r Finding the proportion of successful nesting attempts for each species}
propOR <- prop.table(contingency_trep[1:2, "Olive Ridley"])
propOR

propH <- prop.table(contingency_trep[1:2, "Hawksbill"])
propH

propL <- prop.table(contingency_trep[1:2, "Leatherback"])
propL
```
Of the three species, the Hawksbill nests experienced the highest nest attempt abortion proportion: 0.43. Since this species seems to be having the least nesting success of the three, I would prioritize it for a conservation response.

#Question 13#
```{r reading in the egg count data}
scramble <- read_csv("scrambled_eggs.csv", col_names = (TRUE), col_types = cols(Nest = "f", Species = "f", Eggs = "d"))
scramble
```

#Question 14#
```{r Generating boxplots to compare the number of eggs in each species nests}
d <- ggplot(scramble, aes(x = Species, y = Eggs, fill = Species))
box_of_eggs <-d+geom_boxplot(position = "dodge", show.legend = FALSE)+theme_classic()+geom_jitter(width=0.1,alpha=0.2)+theme(legend.position = "none")+scale_y_continuous("Number of Eggs per Nest")
box_of_eggs
```


#Question 15#
```{r Plotting Leatherback against Hawksbill Egg Counts}
eggscramble <- read_csv("leatherhawk_eggs.csv", col_names = (TRUE), col_types = cols(Hawksbill = "d", Leatherback = "d", Nest = "f"))
eggscramble

e <- ggplot(eggscramble, aes(x = Leatherback, y = Hawksbill, color = Nest))
LeatherHawk <- e+geom_point()+theme_classic()+scale_y_continuous("Number of Eggs per Hawksbill Nest", limits = c(80, 160))+scale_x_continuous("Number of Eggs per Leatherback Nest", limits = c(80,160))
LeatherHawk
```